---
title: "test-seanmmurray-1"
output: html_document
date: "2023-03-19"
---

## retest

#first leaf out / spring tmin
```{r tminspring}
tminspring <- cdf2 %>%
  group_by(year, individual_id, common_name, phenophase_description) %>%
  filter(day_of_year == min(day_of_year),
         phenophase_description == "Leaves")
```

```{r tab4}
tab4 <- tabPanel("BIVARIATE", 
                 fluid = TRUE,
                 sidebarLayout(
                   sidebarPanel(
                     
                     ##Input 1: year(s)
                     selectInput(
                       inputId = "year",
                       label = strong("Select Year"),
                       choices = unique(tminspring$year),
                       selected = "2010"
                     ),
                     
                     ##Input 2: weather condition: tmax spring or tmin spring
                     
                     
                     ##Input 3: species
                     selectInput(
                       inputId = "common_name",
                       label = strong("Select Species"),
                       choices = unique(tminspring$common_name),
                       selected = "yellow birch"
                     ),
                     
                     ##input 4: trendline toggle
                     
                   ),
                   mainPanel(
                     h4("BIVARIATE", align = "center"),
                     plotOutput(outputId = "plot4")
                   )
                 )
)
```

selected_tab4 <- reactive({
    cdf2 %>%
      filter(
        year == input$year,
        common_name == input$common_name,

      )
  })
  
  output$plot4 <- renderPlot({
    plot(
      x = selected_tab4()$tmin_spring,        #tmin spring or tmax spring
      y = selected_tab4()$day_of_year,   #first leaf out (species)
      xlab = "Spring Temperature [min or max]",
      ylab = "First leaf out for [species]"
    )
    abline(fit <-
             lm(selected_status()$day_of_year ~ selected_status()$year),
           col = 'red')
  })
